Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2016-06-16 manuscript/manuscript_pve.Rmd
BM edits

```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize.R")
```  
**Figure 6**. (a) Total C mass of harvested seedlings versus modelled net leaf carbon gain over 120 days. The dashed black line hows the 1:1 line and the dashed red line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling. (b) Carbon use efficiency (ration of final biomass to modelled net leaf C gain) of plants growth in different container sizes.

>>>>

```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize.R")
```  
**Figure 6**. (a) Total C mass of harvested seedlings versus modelled net leaf carbon gain over 120 days. The dashed black line shows the 1:1 line and the dotted black line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling. (b) Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.
